---
title: "lab9_jelia"
author: "James Elia"
date: "10/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(stringr)
```

## Exercise 1
One backslash escapes regular expressisons, a backslash in quotations will be treater as an escape followed by a quotation mark, two backslashes in parentheses will escape from a regular expression and the third backslash will escape you from the string, so four are needed in total.
```{r}
x <- "\"\'\\"
str_view(x, "\"\'\\\\")
```
## Exercise 2
```{r}
str_view(x, "\\$\\^\\$")
str_view(x, "^y")
str_view(x, "x$")
str_view(x, "^...$")
```

## Exercise 3
```{r}
y <- c("apple", "igloo", "dog","CNN", "reed", "sweated", "wise", "crying")
str_view(y, "(^a|^e|^i|^o|^u)")
str_view(y, "[^aeiou]")
str_view(y,c("ed$", "[eed$]"))
str_view(y, c("ie","[cei]"))
str_view(y, "qu")
str_view(y, "colou?r")
str_view(y, "1[ ]//d//d//d[ ]//d//d//d[ ]//d//d//d//d")
```

## Exercise 4
? is equivalent to {,1}
+ is equivalent to {1,}
* is equivalent to {0,}
^.*$ is confusing because it's looking for a phrase that starts with . (any character) and ends with {0,} yet there is nothing in between so wouldn't this count everyhting?
